---
title: "Plots and Analysis for Sciorilli et al. Elasmobranch eDNA paper"
output: html_notebook
---


<br/>

# Table of Contents
- [Load packages](#load-packages)
- [Import and prepare data](#import-and-prepare-data)
- [QC and filtering](#qc-and-filtering)
- [Visualizations](#visualizations)

      
<br/>



# Load packages

```{r}
# rm(list = ls())
library(tidyverse)
library(phyloseq)
library(vegan)
library(RColorBrewer)
library(microbiome)
library(metagMisc)
library(fantaxtic)
library(ggrepel)
library(paletteer)
library(sf)

```

# Map

Import geo data for Shinn bay and make basemap
```{r}
# lets get a box to make a smaller sized objects and facilitate the examples:
geo.box <- c(xmin=-72.61, xmax=-72.4, ymin=40.79, ymax=40.9)

sf_use_s2(FALSE)

# Shoreline data for us detail
gshhg.l1 <- sf::read_sf("raw_data/gshhg-shp-2.3.7/GSHHS_shp/f/GSHHS_f_L1.shp") %>% st_crop(geo.box)
plot(gshhg.l1["id"])

# make ggplot object
shinnbay_map <- ggplot(data = gshhg.l1) +
  geom_sf(aes(geometry = geometry)) +
    scale_x_continuous(breaks = seq(-72.6, -72.4, 0.1)) +
    scale_y_continuous(breaks = seq(40.80, 40.9, 0.05))

shinnbay_map

```

Import station GPS locations and plot ontop of base map
```{r}
station_gps <- read_csv("raw_data/GPS_locations.csv")
station_gps

station_map <- shinnbay_map +
  geom_point(
    data = station_gps,
    aes(x = Lon, y = Lat, color = `Sample Type`),
    size = 4) +
  geom_text_repel(
    data = station_gps,
    aes(x = Lon, y = Lat, label = site_altname),
    size = 3,
    min.segment.length = 0,
    box.padding = 0.25,
    point.padding = 0.25,
    max.overlaps = Inf) +
  scale_color_manual(name = NULL,
                     values = c(Trawl = "chartreuse2",
                                'Oyster reef' = "cadetblue",
                                'Clam sanctuary' = "darkorange")) +
  guides(color = guide_legend(title.position = "top",
      title.hjust = 0.5,
      nrow = 1,
      byrow = TRUE,
      override.aes = list(size = 4))) +
  theme_minimal() +
  theme(legend.position = "bottom",
    legend.direction = "horizontal",
    legend.title = element_blank(),
    legend.text = element_text(size = 9),
    legend.key.width = unit(1.2, "lines"),
    legend.key.height = unit(0.8, "lines",),
    axis.title = element_blank(),)

station_map

ggsave("figure/map.jpg", plot = station_map)

  
```


#  Import and prepare eDNA data

Turn into phyloseq objects

**2021 data**
```{r}
asv_count <- read.delim("revamp_results/results-revamp-2021_Elas02_ASVs_counts.tsv", header=TRUE, stringsAsFactors=FALSE)
row.names(asv_count) <- asv_count$x
asv_count <- asv_count %>% select(-x)
asv_count_mat <- as.matrix(asv_count)

asv_taxonomy <- read.delim("revamp_results/results-revamp-2021_Elas02_asvTaxonomyTable.txt", header=TRUE, stringsAsFactors=FALSE)
row.names(asv_taxonomy) <- asv_taxonomy$ASV
asv_taxonomy <- asv_taxonomy %>% select(-ASV)
asv_taxonomy_mat <- as.matrix(asv_taxonomy)

sample_metadata <- read.delim("revamp_results/results-revamp-2021_Elas02_sample_metadata_forR.txt", header=TRUE, stringsAsFactors=TRUE)
row.names(sample_metadata) <- sample_metadata$Sample
sample_metadata <- sample_metadata %>% select(-Sample)

ASV_2021 = otu_table(asv_count_mat, taxa_are_rows = TRUE)
TAX_2021 = tax_table(asv_taxonomy_mat)
samples_2021 = sample_data(sample_metadata)

phylo_2021 <- phyloseq(ASV_2021, TAX_2021, samples_2021)

```


**2023 data**
```{r}
asv_count <- read.delim("revamp_results/results-revamp-2023_Elas02_ASVs_counts.tsv", header=TRUE, stringsAsFactors=FALSE)
row.names(asv_count) <- asv_count$x
asv_count <- asv_count %>% select(-x)
asv_count_mat <- as.matrix(asv_count)

asv_taxonomy <- read.delim("revamp_results/results-revamp-2023_Elas02_asvTaxonomyTable.txt", header=TRUE, stringsAsFactors=FALSE)
row.names(asv_taxonomy) <- asv_taxonomy$ASV
asv_taxonomy <- asv_taxonomy %>% select(-ASV)
asv_taxonomy_mat <- as.matrix(asv_taxonomy)

sample_metadata <- read.delim("revamp_results/results-revamp-2023_Elas02_sample_metadata_forR.txt", header=TRUE, stringsAsFactors=TRUE)
row.names(sample_metadata) <- sample_metadata$Sample
sample_metadata <- sample_metadata %>% select(-Sample)

ASV_2023 = otu_table(asv_count_mat, taxa_are_rows = TRUE)
TAX_2023 = tax_table(asv_taxonomy_mat)
samples_2023 = sample_data(sample_metadata)

phylo_2023 <- phyloseq(ASV_2023, TAX_2023, samples_2023)

```




# QC and filtering


**2021**
Check some features of the phyloseq object
```{r}
ranks <- rank_names(phylo_2021)
ranks

unique(tax_table(phylo_2021)[, ranks[1]])
unique(tax_table(phylo_2021)[, ranks[2]])
unique(tax_table(phylo_2021)[, ranks[3]])
```

Remove the birds, mammals, and Actinopteri- some of these have exact match to primers, but they are not really subject of study.
```{r}
nrow(tax_table(phylo_2021)) # number of taxa before filtering
ps2021 <- subset_taxa(phylo_2021, !Class == 'Aves' & !Class == 'Mammalia' & !Class == 'Actinopteri')
nrow(tax_table(ps2021)) # number of taxa left
unique(tax_table(ps2021)[, ranks[3]])
```
**2023**
Check some features of the phyloseq object
```{r}
ranks <- rank_names(phylo_2023)
ranks

unique(tax_table(phylo_2023)[, ranks[1]])
unique(tax_table(phylo_2023)[, ranks[2]])
unique(tax_table(phylo_2023)[, ranks[3]])
```

Remove the birds, mammals, and Actinopteri
```{r}
nrow(tax_table(phylo_2023)) # number of taxa before filtering
ps2023 <- subset_taxa(phylo_2023, !Class == 'Aves' & !Class == 'Mammalia' & !Class == 'Actinopteri')
nrow(tax_table(ps2023)) # number of taxa left
unique(tax_table(ps2023)[, ranks[3]])
```


Remove ASVs with low number of reads

```{r}
ps2021 <- metagMisc::phyloseq_filter_sample_wise_abund_trim(
  ps2021,
  minabund = 1000,
  relabund = FALSE)

data.frame(otu_table(ps2021))
```

```{r}
ps2023 <- metagMisc::phyloseq_filter_sample_wise_abund_trim(
  ps2023,
  minabund = 1000,
  relabund = FALSE)

data.frame(otu_table(ps2023))
```


### Manual curation

```{r}
# Replace NA in Species with "Name-of-genus sp."
tax_table(ps2021) <- tax_table(fantaxtic::name_na_taxa(ps2021, include_rank = F, na_label = "<tax> sp."))
tax_table(ps2023) <- tax_table(fantaxtic::name_na_taxa(ps2023, include_rank = F, na_label = "<tax> sp."))

```

replace Pteroplatytrygon sp. with Pteroplatytrygon violacea (there is only one known species in this genus)

```{r}
tax_table(ps2023) <- gsub(tax_table(ps2023), pattern="Pteroplatytrygon sp.", replacement="Pteroplatytrygon violacea")

```


## Agglomerate by taxonomy
Generate new otu tables after grouping ASVs by species name
```{r}
ps2021glommed <- tax_glom(ps2021, "Species")

# plot total reads
plot_bar(ps2021glommed, x = "Sample")

# view tax_table
data.frame(tax_table(ps2021glommed))
```



```{r}
ps2023glommed <- tax_glom(ps2023, "Species")

# plot total reads
plot_bar(ps2023glommed, x = "Sample")

# view tax_table
data.frame(tax_table(ps2023glommed))
```

## Export agglomerated taxonomy-based tables

**2021**
```{r}
elas02_2021_asv_table_taxbased <- data.frame(otu_table(ps2021glommed))
elas02_2021_tax_table_taxbased <- rownames_to_column(data.frame(tax_table(ps2021glommed)), var = "1stRepresentative_ASV")
elas02_2021_sample_data_taxbased <- data.frame(sample_data(ps2021glommed))


# add on common names to tax_table
commonnames <- read_csv(file = "commonnames.csv")
elas02_2021_tax_table_taxbased <- left_join(elas02_2021_tax_table_taxbased, commonnames, by = c("Species" = "Taxon"))

# view
elas02_2021_asv_table_taxbased
elas02_2021_tax_table_taxbased
elas02_2021_sample_data_taxbased

# export
write.csv(elas02_2021_asv_table_taxbased,"figure/elas02_2021_asv_table_taxbased.csv", row.names = TRUE)
write.csv(elas02_2021_tax_table_taxbased,"figure/elas02_2021_tax_table_taxbased.csv", row.names = FALSE)
write.csv(elas02_2021_sample_data_taxbased,"figure/elas02_2021_sample_data_taxbased.csv", row.names = TRUE)
```


**2023**
```{r}
elas02_2023_asv_table_taxbased <- data.frame(otu_table(ps2023glommed))
elas02_2023_tax_table_taxbased <- rownames_to_column(data.frame(tax_table(ps2023glommed)), var = "1stRepresentative_ASV")
elas02_2023_sample_data_taxbased <- data.frame(sample_data(ps2023glommed))

# add on common names to tax_table
commonnames <- read_csv(file = "commonnames.csv")
elas02_2023_tax_table_taxbased <- left_join(elas02_2023_tax_table_taxbased, commonnames, by = c("Species" = "Taxon"))

# view
elas02_2023_asv_table_taxbased
elas02_2023_tax_table_taxbased
elas02_2023_sample_data_taxbased

# export
write.csv(elas02_2023_asv_table_taxbased,"figure/elas02_2023_asv_table_taxbased.csv", row.names = TRUE)
write.csv(elas02_2023_tax_table_taxbased,"figure/elas02_2023_tax_table_taxbased.csv", row.names = FALSE)
write.csv(elas02_2023_sample_data_taxbased,"figure/elas02_2023_sample_data_taxbased.csv", row.names = TRUE)
```



Also calculate *relative abundances* (# of ASV sequences/sum total sequences in sample), for some plotting

```{r}
ps2021_ra <- microbiome::transform(ps2021, transform = "compositional")
ps2021glommed_ra <- microbiome::transform(ps2021glommed, transform = "compositional")

ps2023_ra <- microbiome::transform(ps2023, transform = "compositional")
ps2023glommed_ra <- microbiome::transform(ps2023glommed, transform = "compositional")

```

# Visualizations

## Set up dataframes

```{r}
# convert ps object to dataframe using phyloseq's psmelt
ps2021glommed_df <- psmelt(ps2021glommed)
ps2023glommed_df <- psmelt(ps2023glommed)
ps2021glommed_ra_df <- psmelt(ps2021glommed_ra)
ps2023glommed_ra_df <- psmelt(ps2023glommed_ra)

# replace zeroes in the table with NA
ps2021glommed_df[ps2021glommed_df == 0] <- NA
ps2023glommed_df[ps2023glommed_df == 0] <- NA
ps2021glommed_ra_df[ps2021glommed_ra_df == 0] <- NA
ps2023glommed_ra_df[ps2023glommed_ra_df == 0] <- NA

# and remove rows with NAs (so they don't appear as small dots in plot)
ps2021glommed_df <-  filter(ps2021glommed_df, !is.na(Abundance))
ps2023glommed_df <-  filter(ps2023glommed_df, !is.na(Abundance))
ps2021glommed_ra_df <-  filter(ps2021glommed_ra_df, !is.na(Abundance))
ps2023glommed_ra_df <-  filter(ps2023glommed_ra_df, !is.na(Abundance))

# add in common names
ps2021glommed_df <- left_join(ps2021glommed_df, commonnames, by = c("Species" = "Taxon"))
ps2023glommed_df <- left_join(ps2023glommed_df, commonnames, by = c("Species" = "Taxon"))
ps2021glommed_ra_df <- left_join(ps2021glommed_ra_df, commonnames, by = c("Species" = "Taxon"))
ps2023glommed_ra_df <- left_join(ps2023glommed_ra_df, commonnames, by = c("Species" = "Taxon"))

# and view
ps2021glommed_df
ps2023glommed_df
ps2021glommed_ra_df
ps2023glommed_ra_df
```




## Set fill colors

```{r}
# set colors so Com name and Sp name are consistent colors across plots
fill_map <- dplyr::bind_rows(ps2021glommed_df %>% 
                               select(Taxon.CommonName, Color),ps2023glommed_df %>% 
                               select(Taxon.CommonName, Color)) %>%
  distinct(Taxon.CommonName, .keep_all = TRUE) %>%
  tibble::deframe()

fill_map
```






## Examine controls 
Plot positive controls
```{r}
label_map <- c(
  AMW_S2      = "Aquarium",
  CCE1        = "S. retifer tank 1",
  CCE2        = "S. retifer tank 2",
  MC1         = "M. canis tissue",
  SA1         = "S. acanthias tissue",
  Shark_blood = "M. canis blood"
)

# Helper- wraps labels on plot
wrap_labels <- function(x, width = 12) {
  lab <- label_map[x]
  lab[is.na(lab)] <- x[is.na(lab)]
  str_wrap(lab, width = width)}

# plot
ps2021_posctl_barplot <- ggplot(ps2021glommed_df %>% filter(controls == "positive"),
  aes(x = replicates, y = Abundance, fill = Taxon.CommonName)) +
  geom_col() +
  theme_bw() +
  scale_y_continuous(name = "Read Abundance") +
  scale_x_discrete(labels = function(x) wrap_labels(x, width = 12)) +
  scale_fill_manual(values = fill_map) +
  labs(fill = NULL) +
  theme(axis.title.x=element_blank(),
        axis.text.x = element_text(size = 8),
        axis.text.y = element_text(size = 8),
        legend.title = element_text(size = 9),
        legend.text  = element_text(size = 8))


ps2021_posctl_ra_barplot <- ggplot(
  ps2021glommed_ra_df %>% filter(controls == "positive"),
  aes(x = replicates, y = Abundance, fill = Taxon.CommonName)
) +
  geom_col() +
  theme_bw() +
  scale_y_continuous(name = "Relative Abundance") +
  scale_x_discrete(labels = function(x) wrap_labels(x, width = 12)) +
  scale_fill_manual(values = fill_map) +
  labs(fill = NULL) +
  theme(axis.title.x=element_blank(),
        axis.text.x = element_text(size = 8),
        axis.text.y = element_text(size = 8),
        legend.title = element_text(size = 9),
        legend.text  = element_text(size = 8))

ps2021_posctl_barplot
ps2021_posctl_ra_barplot




# save
ggsave(plot = ps2021_posctl_barplot, filename = "figure/2021_posctl_barplot.eps", width = 180, height = 75, units = "mm")
ggsave(plot = ps2021_posctl_barplot, filename = "figure/2021_posctl_barplot.jpg", width = 180, height = 75, units = "mm")
ggsave(plot = ps2021_posctl_ra_barplot, filename = "figure/2021_posctl_ra_barplot.eps", width = 180, height = 75, units = "mm")
ggsave(plot = ps2021_posctl_ra_barplot, filename = "figure/2021_posctl_ra_barplot.jpg", width = 180, height = 75, units = "mm")




# export data of pos ctls for text of manuscript
ps2021_posctls <- data.frame(otu_table(subset_samples(ps2021glommed, controls == "positive")))
ps2021_posctls_ra <- data.frame(otu_table(subset_samples(ps2021glommed_ra, controls == "positive")))
ps2021_posctls_taxa <- data.frame(tax_table(subset_samples(ps2021glommed, controls == "positive")))

write.csv(ps2021_posctls, file = "figure/ps2021_posctls.csv")
write.csv(ps2021_posctls_ra, file = "figure/ps2021_posctls_ra.csv")
write.csv(ps2021_posctls_taxa, file = "figure/ps2021_posctls_taxa.csv")

```






## Bubble plots

Based on previous [scripts](https://github.com/lizsuter/Cariaco_Euk)



Plot by species, scientific name
**2021**
```{r}

# pull out and order site names
levels(unique(c(ps2021glommed_df$sites, ps2023glommed_df$sites)))
# reorder to
sitelevels <- c("1","2","3","4","5","6","7","8","9","10","11","12","13","TI","WC", "C4", "C5", "S1", "S3","S6", "S9")

# order bayside so it is geographically W-E and not alphabetical, E-W
ps2021glommed_df <- ps2021glommed_df %>% mutate(BAYSIDE = factor(BAYSIDE, levels = c("WEST", "EAST")))
ps2021glommed_ra_df <- ps2021glommed_ra_df %>% mutate(BAYSIDE = factor(BAYSIDE, levels = c("WEST", "EAST")))


# 2021, read abundance
bubbleplot_2021 <- ggplot(ps2021glommed_df %>% filter(is.na(controls)), aes(x = factor(sites, levels = sitelevels), y = fct_rev(Taxon.CommonName))) + # fct_rev helps to present it in reverse order in the plot (from top to btm alphabetically)
  geom_point(aes(size=ifelse(Abundance==0, NA, Abundance), fill = Taxon.CommonName), color = "black", pch = 21) +
  scale_size_area(breaks = c(1000,10000,100000,1000000,10000000))+
  xlab("")+
  ylab("")+
  labs(size="Read Abundance", fill = "")+
  theme_bw() +
  scale_fill_manual(values = fill_map) +
  theme(axis.title.x=element_blank(),
        axis.text.x = element_text(size = 8),
        axis.text.y = element_text(size = 8),
        legend.title = element_text(size = 9),
        legend.text  = element_text(size = 8)) +
  facet_grid(Month~BAYSIDE, scales = "free", space = "free", drop= TRUE) +
  guides(fill = "none")


# 2021, relative abundance
bubbleplot_2021_ra <- ggplot(ps2021glommed_ra_df %>% filter(is.na(controls)), aes(x = factor(sites, levels = sitelevels), y = fct_rev(Taxon.CommonName))) +
  geom_point(aes(size=ifelse(Abundance==0, NA, Abundance), fill = Taxon.CommonName), color = "black", pch = 21) +
  scale_size_area(breaks = c(.25,.5,.75,1), max_size = 6)+
  xlab("")+
  ylab("")+
  labs(size="Relative Abundance", fill = "")+
  theme_bw() +
  scale_fill_manual(values = fill_map) +
  theme(axis.title.x=element_blank(),
        axis.text.x = element_text(size = 8),
        axis.text.y = element_text(size = 8),
        legend.title = element_text(size = 9),
        legend.text  = element_text(size = 8)) +
  facet_grid(Month~BAYSIDE, scales = "free", space = "free", drop= TRUE) +
  guides(fill = "none")



bubbleplot_2021
bubbleplot_2021_ra


# save
ggsave(plot = bubbleplot_2021, filename = "figure/bubbleplot_2021.eps", width = 180, height = 180, units = "mm")
ggsave(plot = bubbleplot_2021, filename = "figure/bubbleplot_2021.jpg", width = 180, height = 180, units = "mm")
ggsave(plot = bubbleplot_2021_ra, filename = "figure/bubbleplot_2021_ra.eps", width = 180, height = 180, units = "mm")
ggsave(plot = bubbleplot_2021_ra, filename = "figure/bubbleplot_2021_ra.jpg", width = 180, height = 180, units = "mm")
```


**2023**
```{r}
# order bayside so it is geographically W-E and not alphabetical, E-W
ps2023glommed_df <- ps2023glommed_df %>% mutate(BAYSIDE = factor(BAYSIDE, levels = c("WEST", "EAST")))
ps2023glommed_ra_df <- ps2023glommed_ra_df %>% mutate(BAYSIDE = factor(BAYSIDE, levels = c("WEST", "EAST")))


# 2023, read abundance
bubbleplot_2023 <- ggplot(ps2023glommed_df %>% filter(is.na(controls)), aes(x = factor(sites, levels = sitelevels), y = fct_rev(Taxon.CommonName))) + # fct_rev helps to present it in reverse order in the plot (from top to btm alphabetically)
  geom_point(aes(size=ifelse(Abundance==0, NA, Abundance), fill = Taxon.CommonName), color = "black", pch = 21) +
  scale_size_area(breaks = c(1000,10000,100000,1000000,10000000))+
  xlab("")+
  ylab("")+
  labs(size="Read Abundance", fill = "")+
  theme_bw() +
  scale_fill_manual(values = fill_map) +
  theme(axis.title.x=element_blank(),
        axis.text.x = element_text(size = 8),
        axis.text.y = element_text(size = 8),
        legend.title = element_text(size = 9),
        legend.text  = element_text(size = 8)) +
  facet_grid(Month~BAYSIDE, scales = "free", space = "free", drop= TRUE) +
  guides(fill = "none")


# 2023, relative abundance
bubbleplot_2023_ra <- ggplot(ps2023glommed_ra_df %>% filter(is.na(controls)), aes(x = factor(sites, levels = sitelevels), y = fct_rev(Taxon.CommonName))) +
  geom_point(aes(size=ifelse(Abundance==0, NA, Abundance), fill = Taxon.CommonName), color = "black", pch = 21) +
  scale_size_area(breaks = c(.25,.5,.75,1), max_size = 6)+
  xlab("")+
  ylab("")+
  labs(size="Relative Abundance", fill = "")+
  theme_bw() +
  scale_fill_manual(values = fill_map) +
  theme(axis.title.x=element_blank(),
        axis.text.x = element_text(size = 8),
        axis.text.y = element_text(size = 8),
        legend.title = element_text(size = 9),
        legend.text  = element_text(size = 8)) +
  facet_grid(Month~BAYSIDE, scales = "free", space = "free", drop= TRUE) +
  guides(fill = "none")



bubbleplot_2023
bubbleplot_2023_ra


# save
ggsave(plot = bubbleplot_2023, filename = "figure/bubbleplot_2023.eps", width = 180, height = 140, units = "mm")
ggsave(plot = bubbleplot_2023, filename = "figure/bubbleplot_2023.jpg", width = 180, height = 140, units = "mm")
ggsave(plot = bubbleplot_2023_ra, filename = "figure/bubbleplot_2023_ra.eps", width = 180, height = 140, units = "mm")
ggsave(plot = bubbleplot_2023_ra, filename = "figure/bubbleplot_2023_ra.jpg", width = 180, height = 140, units = "mm")
```




## Time Series Plots
Look at total read abundance and rel abundance for different spp per month. Aggregate sites by bayside (E/W) and type (open water/ bivalve habitat)

**2021**
```{r}
# First group total reads by Species, Habitat_type and Month so there is one point per time point on the plot
TimeSeries_df_2021 <- ps2021glommed_df %>% filter(is.na(controls)) %>%
  group_by(Month, Habitat_type, Taxon.CommonName) %>%
  summarise(TotalReads = sum(Abundance))
TimeSeries_df_2021
```


```{r}
#force the order of Habitat type so it plots in desired order
TimeSeries_df_2021$Habitat_type_f = factor(TimeSeries_df_2021$Habitat_type, levels=c("OPEN WATER", "CLAM SANCTUARY"))

speciestimeseries_comname_2021 <- ggplot(TimeSeries_df_2021, aes(x = Month, y = log10(TotalReads))) +
  geom_col(aes(fill = Taxon.CommonName), show.legend = FALSE) +
  ylab("Log 10 (Reads)")+
  theme_bw() +
  theme(axis.title.x=element_blank(),
        legend.title=element_blank(),
        axis.text.x = element_text(size = 8),
        axis.text.y = element_text(size = 8),
          strip.text = element_text(size = 8)) +
  scale_x_continuous(breaks=c(5,6,7,8,9,10), labels = c("M","J","J","A","S","O")) +
  facet_grid(Habitat_type_f~Taxon.CommonName,
             labeller = labeller(Taxon.CommonName = label_wrap_gen(width = 12))) +
  scale_fill_manual(values = fill_map)


speciestimeseries_comname_2021
ggsave(speciestimeseries_comname_2021, filename = "figure/speciestimeseries_2021.jpg", height = 90, width = 250, units = "mm")
```






**2023**
```{r}
# First group total reads by Species, Habitat_type and Month so there is one point per time point on the plot
TimeSeries_df_2023 <- ps2023glommed_df %>% filter(is.na(controls)) %>%
  group_by(Month, Habitat_type, Taxon.CommonName) %>%
  summarise(TotalReads = sum(Abundance))
TimeSeries_df_2023
```


```{r}
#First force the order of Habitat type so it plots in desired order
TimeSeries_df_2023$Habitat_type_f = factor(TimeSeries_df_2023$Habitat_type, levels=c("OYSTER REEF","OPEN WATER", "CLAM SANCTUARY"))

speciestimeseries_comname_2023 <- ggplot(TimeSeries_df_2023, aes(x = Month, y = log10(TotalReads))) +
  geom_col(aes(fill = Taxon.CommonName), show.legend = FALSE) +
  ylab("Log 10 (Reads)")+
  theme_bw() +
  theme(axis.title.x=element_blank(),
        legend.title=element_blank(),
        axis.text.x = element_text(size = 8),
        axis.text.y = element_text(size = 8),
          strip.text = element_text(size = 8)) +
  scale_x_continuous(breaks=c(5,6,7,8,9), labels = c("M","J","J","A","S")) +
  facet_grid(Habitat_type_f~Taxon.CommonName,
             labeller = labeller(Taxon.CommonName = label_wrap_gen(width = 8))) +
  scale_fill_manual(values = fill_map)


speciestimeseries_comname_2023
ggsave(speciestimeseries_comname_2023, filename = "figure/speciestimeseries_2023.jpg", height = 120, width = 250, units = "mm")
```








